### 2021-11-20 draft.tex
Deploying to gh-pages from @ gottacatchenall/thesis_proposal@ae104464ff5a0ac19d1b58a70d83427601ec710a 🚀

However, robust forecasting of ecological processes will change in the
future is, to say the least, quite difficult. This difficultly is
compounded by a few factors, the first being that sampling ecosystems is
not easy. Ecological data is often biased, and noisey, spatially and
temporally sparse. As a result \emph{ecosystem monitoring} (Makiola
\emph{et al.} 2020) has emerged as an imperative. Developing a system
for ecological observation, which is able to coordinate across
locations. (\textbf{AndyUrbanBiomonitoring?} paper).

@@

Although it is become almost hack to complain about the dang weather
forecast being wrong, over the least 50 years the
(\textbf{Bauer2015QuiRev?}).

@@

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Building an interaction prediction model.
\item
  Make it spatial based on distributions.
\item
  Forecast distributions based on CMIP6.
\end{enumerate}

@@

\hypertarget{ch2-optimizing-sampling-of-interactions}{%
\section{CH2 optimizing sampling of
interactions}\label{ch2-optimizing-sampling-of-interactions}}

This chapter quantifies the relationship between a given species
relative abundance and the sampling effort needed to adequately
understand this species distribution and interactions.

For a given sample of interaction data, and proposes a method for
optimizing spatial sampling of a possible interaction between species as
a function of the estimated distribution of both species.

@@

\begin{itemize}
\item
  the missing link paper, turn this into optimizing with two different
  SDMs
\item
  relative abundance and its effect on false negative
\item
  non-independent associations in samples
\item
  simulate species distribution and efficacy of detection given a set of
  observation points where the dist from observation site decays.
\item
  optimize set of repeated sampling locations L for a \emph{known}
  distribution D.
\item
  address SDM not being the territory
\end{itemize}

@@

@@

\begin{itemize}
\tightlist
\item
  land cover -\textgreater{} resistance -\textgreater{} extinction time
\item
  simulated annealing to optimize landscape optimization
\end{itemize}

@@

\begin{itemize}
\item
  TK conceptual figure with interfaces between what I'm writing / have
  contributed to and linked with other libraries
\item
  \texttt{Observatories.jl}, \texttt{Corridors.jl}, \texttt{MCD.jl}
\end{itemize}

\hypertarget{concl}{%
\section{concl}\label{concl}}

// this is a discussion para An oft applied definition of the origin of
is ``the application of the scientific method to natural history.''
Since its origin ecology has been a descriptive science. This is a
natural by-product of the immense variability of Earth's biosphere.
emerged to explain particular phenomena at particular scales. In recent
years, there has been an interest in an epistemological shift in
ecology. To shift ecology into a predictive science. The justification
for this shift is twofold: (1) bogged down philosophy of science, by
further rooting our understanding of ecosystem function and dynamics in
an ability to predict their structure (Dietze 2017). and (2) the
practical need for models for \emph{ecological forecasting}.

@@

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Chen2019RevCom}{}%
Chen, Y., Angulo, M.T. \& Liu, Y.-Y. (2019). Revealing Complex
Ecological Dynamics via Symbolic Regression. \emph{BioEssays}, 41,
1900069.

@@

>>>>

However, robust forecasting of ecological processes will change in the
future is, to say the least, quite difficult (Beckage \emph{et al.}
2011; Petchey \emph{et al.} 2015). This difficultly is compounded by a
few factors, the first being that sampling ecosystems is not easy.
Ecological data is often biased, and noisey, spatially and temporally
sparse. As a result \emph{ecosystem monitoring} (Makiola \emph{et al.}
2020) has emerged as an imperative. Developing a system for ecological
observation, which is able to coordinate across locations.
(\textbf{AndyUrbanBiomonitoring?} paper).

@@

Although it is become almost hack to complain about the dang weather
forecast being wrong, over the least 50 years the (Bauer \emph{et al.}
2015).

@@

The data for this chapter is derived from multiple souces and can be
split into three categories. (1) Field data from three different
locations acvross Colorado. All field sites have multiple plots across
an elevational gradient.

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\tightlist
\item
  Building an interaction prediction model. 2) Make it spatial based on
  distributions. 3) Forecast distributions based on CMIP6.
\end{enumerate}

@@

\hypertarget{chapter-two-optimizing-spatial-sampling-of-species-interactions}{%
\section{Chapter Two: Optimizing spatial sampling of species
interactions}\label{chapter-two-optimizing-spatial-sampling-of-species-interactions}}

There are false-negatives in interation data. Co-occurrence is not the
same thing as interaction (\textbf{cite?}), but often is used as a
proxy.

This chapter unravels the relationship between a given species relative
abundance and the sampling effort needed to adequately understand this
species distribution and interactions.

There is more than one way to observe a false-negative.

\begin{figure}
\centering
\includegraphics{./figures/ch2.png}
\caption{taxonomy of false negatives}
\end{figure}

@@

\begin{itemize}
\item
  the missing link paper, turn this into optimizing with two different
  SDMs relative abundance and its effect on false negative
  non-independent associations in samples
\item
  simulate species distribution and efficacy of detection given a set of
  observation points where the dist from observation site decays.
  optimize set of repeated sampling locations L for a \emph{known}
  distribution D. address SDM not being the territory
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  nonrandom association figure sampling effort under neutral model
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  land cover -\textgreater{} resistance -\textgreater{} extinction time
  simulated annealing to
\item
  optimize landscape optimization
\end{itemize}

@@

\begin{itemize}
\item
  TK conceptual figure with interfaces between what I'm writing / have
\item
  contributed to and linked with other libraries
\item
  \texttt{Observatories.jl}, \texttt{Corridors.jl}, \texttt{MCD.jl}
\end{itemize}

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

@@

\begin{figure}
\centering
\includegraphics{./figures/trees.png}
\caption{trees}
\end{figure}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bauer2015QuiRev}{}%
Bauer, P., Thorpe, A. \& Brunet, G. (2015). The quiet revolution of
numerical weather prediction. \emph{Nature}, 525, 47--56.

\leavevmode\hypertarget{ref-Beckage2011LimPre}{}%
Beckage, B., Gross, L.J. \& Kauffman, S. (2011). The limits to
prediction in ecological systems. \emph{Ecosphere}, 2, art125.

\leavevmode\hypertarget{ref-Chen2019RevCom}{}%
Chen, Y., Angulo, M.T. \& Liu, Y.-Y. (2019). Revealing Complex
Ecological Dynamics via Symbolic Regression. \emph{BioEssays}, 41,
1900069.

@@

\leavevmode\hypertarget{ref-Petchey2015EcoFor}{}%
Petchey, O.L., Pontarp, M., Massie, T.M., Kéfi, S., Ozgul, A.,
Weilenmann, M., \emph{et al.} (2015). The ecological forecast horizon,
and examples of its uses and determinants. \emph{Ecology Letters}, 18,
597--611.
